---
title: "Tidy-Tuesday-28-Coffee"
author: "MAJ Daniel Baller"
date: "7/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
Loading packages
```{r}
library(tidyverse)
library(ggcharts)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(rgeos)
library(ggthemes)
library(hrbrthemes)
library(ggthemr)
library(ggdark)
library(magick)
library(cowplot)
library(ggridges)
library(ggpomological)
library(istack)
library(ggbeeswarm)
library(patchwork)
```

Reading in data
```{r}
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```

Saving Data
```{r}
write_csv(coffee_ratings, "week28_coffee_ratings.csv")
```

Lolypop and dumbbell charts of average total cup points by country
```{r}
coffee_ratings %>% 
  filter(country_of_origin != "NA") %>% 
  group_by(country_of_origin) %>% 
  summarize(Mean = mean(total_cup_points), min = min(total_cup_points), max = max(total_cup_points)) %>% 
  lollipop_chart(x = country_of_origin, y = Mean) +
  labs(
    x = "Country",
    y = "Total Cup Points",
    title = "Average cupping score"
  ) #+
#  scale_x_continuous(limits = c(6, 9))

coffee_ratings %>% 
  filter(country_of_origin != "NA") %>% 
  filter(cupper_points > .1) %>% 
  group_by(country_of_origin) %>% 
  summarize(Mean = mean(total_cup_points), min = min(total_cup_points), max = max(total_cup_points)) %>% 
  dumbbell_chart(x = country_of_origin, 
                y1 = min, 
                y2 = max, 
                top_n = 25,
                point_colors = c("lightgray", "#494F5C")) +
  labs(
    x = "Country",
    y = "Total Cup Points",
    title = "Total cup points by country"
  )+
  theme_modern_rc()
```

Dumbbell plot of average total cup points by variety
```{r}
coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points > .1) %>% 
  group_by(variety) %>% 
  summarize(Mean = mean(total_cup_points), min = min(total_cup_points), max = max(total_cup_points)) %>% 
  dumbbell_chart(x = variety, 
                y1 = min, 
                y2 = max,
                top_n = 20,
                point_colors = c("lightgray", "#494F5C")) +
  labs(
    x = "Variety",
    y = "Total Cup Points",
    title = "Average cupping score"
  ) +
  theme_()
```

Boxplots of flavor by country.  Trying to get a background image to work
```{r}
coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot()+geom_boxplot(aes(y = flavor, x = variety, fill = variety))+
  coord_flip()+
  theme_classic()

coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot(aes(color = variety))+geom_beeswarm(aes(y = total_cup_points, x = variety, fill = variety), dodge.width=.8,cex=2)+
  coord_flip()+
  theme_classic()

img <-  %>%
  image_resize("570x380") %>%
  image_colorize(35, "white")

    img = "https://images.unsplash.com/photo-1447933601403-0c6688de566e?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=956&q=80"

ggdraw() + 
  draw_image(img) + 
  draw_plot(p)
```

Scatter plot of aroma vs flavor, colored by total cup points
```{r}
coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot()+geom_point(aes(x = aroma, y = flavor, color = total_cup_points))+
  scale_color_gradient(low = "white", high = "chocolate4")+
  labs(x = "Aroma Grade", y = "Flavor Grade", color = "Cupper Points", 
       title = "How flavor and aroma affect coffee grading", caption = "@danielpballer")+
  dark_theme_classic()
 
coffee_ratings %>% 
  group_by(country_of_origin) %>% count() %>% 
  arrange(desc(n))

```

Ridge plot of cupper point density by country
```{r}
 coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>%  
  count(country_of_origin, sort = T) %>% 
  filter(n>5) %>% 
  select(country_of_origin)->country

 coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  filter(country_of_origin %in% country$country_of_origin) %>% 
  mutate(country_of_origin = as.factor(country_of_origin)) %>% 
  mutate(country_of_origin = fct_reorder(country_of_origin, total_cup_points, .fun = 'max')) %>% 
ggplot(aes(x = total_cup_points, y = country_of_origin, fill = stat(x)))+ 
  #scale_fill_gradient(low = "white", high = "chocolate4")+
  scale_fill_viridis_c(option = "C")+
  labs(x = "Total Cup Points", y = "Country", color = "Cupper points", title = "Distribution of Total Cup Points By Country", subtitle = "Countries are in order of max total cup points.  Black line shows median of each distribution.",  fill = "Total Cup Points", caption = "@danielpballer")+
  geom_density_ridges_gradient(scale = 3, quantile_lines = TRUE, quantiles = 2, color = "black")+
  #theme_solarized_2()
  # theme(plot.title=element_text(size=30))
  dark_theme_classic()

a+plot_annotation(title = "Density curves of Total Cup Points By Country")
```

```{r}

coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot(aes(fill = variety)) + 
        geom_tile(color = "black", size = 0.5) 
```

```{r}
coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot()+
  geom_bar(aes(y = country_of_origin, fill=variety), width = 0.5) + 
  #theme(axis.text.x = element_text(angle=65, vjust=0.6)) +
  labs(title="Variety of coffee by Country", 
       subtitle="count", 
       caption="@danielpballer")+
  dark_theme_classic()

coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>% 
  ggplot()+
  geom_bar(aes(y = country_of_origin, fill=variety), width = 0.5) + 
  #theme(axis.text.x = element_text(angle=65, vjust=0.6)) +
  labs(title="Variety of coffee by Country", 
       subtitle="count", 
       caption="@danielpballer")
 # dark_theme_classic()
```

Diverging normalized lolypop chart average total cup points by country
```{r}
coffee_ratings %>% 
  filter(country_of_origin != "NA") %>% 
  group_by(country_of_origin) %>% 
  summarize(Mean = mean(total_cup_points), min = min(total_cup_points), max = max(total_cup_points)) %>%
  mutate(Mean = scale(Mean)) %>% 
diverging_lollipop_chart(
  x = country_of_origin,
  y = Mean,
  lollipop_colors = c("#006400", "#b32134"),
  text_color = c("#006400", "#b32134")
)
```

tried making a pictogram. didn't work
```{r}
 coffee_ratings %>% 
  filter(variety != "NA") %>% 
  filter(cupper_points>0.1) %>%  
  count(country_of_origin, sort = T) %>% 
  filter(n>5) %>% 
  select(country_of_origin)->country 
  
coffee_ratings %>% 
  filter(country_of_origin %in% country$country_of_origin) %>% 
  istack(var = 'country_of_origin', 
            group = 'variety', 
            icon = "https://image.flaticon.com/icons/svg/31/31082.svg",
            size = 0.025,
            asp = 3)
```

